### 2020-01-27 experiments.tex
Ok

\begin{itemize}
\item {\bf RQ1:}  Does mutation analysis of static analysis tools produce actionable results?  That is, do raw mutation kills serve to distinguish tools from each other, or are all tools similar in terms of mutation detection capability?
\item {\bf RQ2:}  Does our approach provide additional information beyond simply counting findings for the original, un-mutated analyzed code?  Do \emph{ratios} differ between programs, or does the number of mutants killed simply reflect the ``verbosity'' of each tool?
\item {\bf RQ3:}  Do the rankings that raw kills and ratios establish agree with other sources of information about the effectiveness of the evaluated tools?  Can we confirm results from other evaluation methods, or informal opinion?
\item {\bf RQ4:}  Do mutation scores for clean programs differ from those for programs for which tools report findings before mutation?
\item {\bf RQ5:}  Do individual mutants, prioritized for ease of examination, allow us to identify classes of faults that
 different tools are good at/bad at?  Can we extend this information to improve tools by addressing identified weaknesses?
\item {\bf RQ6:}  How easy is it identify low-hanging fruit for improving tools without prioritization to remove conceptually redundant mutants?
  \end{itemize}

In particular, we consider {\bf RQ2} to be of critical importance; if the mutant ratios for tools differ, then this is clear evidence that our hypothesis that the tendency of mutants to be faults, and to expect that mutated code will, by a sound and precise tool, be flagged as problematic more often than non-mutated code, holds.  This expectation that (some subset of the) mutants can serve as proxies for real, detectable faults is the core concept of our approach.
{\bf RQ4} addresses a concern briefly mentioned in the introduction:  it is possible that warnings for the original code interfere with our definition of detection.  The ideal case for our approach is when a tool report no findings for un-mutated code, and either reports a finding (kills the mutant) or not (does not kill it) when the mutant is introduced.  Chekam et al. showed that the ``clean program assumption'' for testing, the idea that coverage will be similar for faulty and fixed versions of a program, is a threat to the validity of investigations of the relationship between coverage and fault detection \cite{CleanProgram}, and we want to establish that this is unlikely to be the case for our approach.
{\bf RQ5} and {\bf RQ6} receive only preliminary answers, for the smart contract tools.

>>>>

\begin{itemize}
\item {\bf RQ1:}  Does mutation analysis of static analysis tools produce actionable results?  That is, do raw mutation kills serve to distinguish tools from each other, or are all tools similar in terms of mutation detection capability?
\item {\bf RQ2:}  Does our approach provide additional information beyond simply counting findings for the original, un-mutated analyzed code?  Do \emph{ratios} differ between programs, or does the number of mutants killed simply reflect the ``verbosity'' of each tool?
\item {\bf RQ3:}  Do the rankings that raw kills and ratios establish agree with other sources of information about the effectiveness of the evaluated tools?  Can we confirm results from other evaluation methods, or informal opinion?
\item {\bf RQ4:}  Are mutation scores for clean programs better than those for programs for which tools report findings before the program is mutated?
\item {\bf RQ5:}  Do individual mutants, prioritized for ease of examination, allow us to identify classes of faults that
 different tools are good at/bad at, and extend this information to improve tools by addressing identified weaknesses?
\item {\bf RQ6:}  How easy is it identify low-hanging fruit for improving tools \emph{without} prioritization to remove conceptually redundant mutants?
  \end{itemize}

In particular, we consider {\bf RQ2} to be of critical importance; if the mutant ratios for tools differ, then this is clear evidence that our hypothesis that the tendency of mutants to be faults, and to expect that mutated code will, by a more precise and accurate tool, be flagged as problematic more often than non-mutated code, holds.  This expectation that (some subset of the) mutants can serve as proxies for real, detectable faults is the core concept of our approach.
{\bf RQ4} addresses a concern briefly mentioned in the introduction:  it is possible that warnings for the original code interfere with our definition of detection.  The ideal case for our approach is when a tool report no findings for un-mutated code, and either reports a finding (kills the mutant) or not (does not kill it) when the mutant is introduced.  Chekam et al. showed that the ``clean program assumption'' for testing, the idea that coverage will be similar for faulty and fixed versions of a program, is a threat to the validity of investigations of the relationship between coverage and fault detection \cite{CleanProgram}, and we want to establish that this is unlikely to be the case for our approach.
{\bf RQ5} and {\bf RQ6} receive only preliminary answers, for the smart contract tools.

### 2020-01-27 introduction.tex
Ok

We can say that a static analysis tool kills a mutant when the number of non-informational or optimization related, that is fault-related, warnings or errors produced with respect to the code \emph{increases} for the mutated version, compared to the original code.  This difference may be most informative and easily interpreted when the original code produces no warnings or errors; we call such code ``clean''. For non-clean code, a tool conceivably could detect the mutant, but only change a previously generated warning, not add an additional warning, leading to an underestimate of effectiveness.  However, even for non-clean code, most detected mutants should produce a new warning.

@@

Second, and critically, this is an \emph{automatable} method that can provide an evaluation of static analysis tools over a large number of target source code files, without requiring human effort to classify results as real bugs or false positives.  It is not clear that any other fully automatic method is competitively meaningful; it is possible that methods based on code changes from version control provide some of the same benefits, but these require classification of changes into bug-fixes and non-bug-fixes, and of course require version control history.  Also, history-based methods will be biased towards precisely those faults humans or tools already in use were able to detect and fix.

>>>>

We can say that a static analysis tool kills a mutant when the number of warnings or errors, which we call \emph{findings}, that are not informational or optimization related, i.e., that are \emph{fault-related}, produced with respect to the code \emph{increases} for the mutated version, compared to the original code. That is, when the tool finds more bugs for the mutated code.  This difference may be most easily interpreted when the original code produces no findings; we call such code \emph{clean}. For non-clean code, a tool conceivably could detect the mutant, but only change a previously generated finding, not add an additional finding, leading to an underestimate of effectiveness.  However, even for non-clean code, \emph{most detected mutants should produce a new warning}.

@@

Second, and critically, this is an \emph{automatable} method that can provide an evaluation of static analysis tools over a large number of target source code files, without requiring human effort to classify results as real bugs or false positives.  It is not clear that any other fully automatic method is competitively meaningful; it is possible that methods based on code changes from version control provide some of the same benefits, but these require classification of changes into bug-fixes and non-bug-fixes, and of course require version control history.  Also, history-based methods will be biased towards precisely those faults humans or tools already in use were able to detect and fix.  Rather than the hundreds \cite{just2014defects4j} or at most few thousand of faults \cite{BugSwarm} in benchmark defect sets, our approach enables the use of \emph{many tens of thousands} of hypothetical faults.

### 2020-01-27 prioritizing.tex
Ok

$$ 5.0 \times r(\mathit{edit}_1, \mathit{edit}_2) +$$
$$0.1 \times r(\mathit{source}_1, \mathit{source}_2) +$$
$$0.1 \times r(\mathit{mutant}_1, \mathit{mutant}_2) +$$
$$0.5 \times \mathit{different\_files} +$$
$$max(0.25, \frac{\mathit{line\_distance}(\mathit{mutant}_1, \mathit{mutant}_2)}{10})$$

\noindent Where $r$ is a Levenshtein-based string similarity ratio,
and $\mathit{line\_distance}$ is the distance in a source file between
two locations, in lines (and zero if the locations are in different
source files).

>>>>

$$ 5.0 \times r(\mathit{edit}_1, \mathit{edit}_2) +$$
$$0.1 \times r(\mathit{source}_1, \mathit{source}_2) +$$
$$0.1 \times r(\mathit{mutant}_1, \mathit{mutant}_2) +$$
$$0.5 \times \mathit{not\_same\_file} +$$
$$max(0.25, \frac{\mathit{line\_dist}(\mathit{mutant}_1, \mathit{mutant}_2)}{10})$$

\noindent Where $r$ is a Levenshtein-based string similarity ratio,
$\mathit{line\_dist}$ is the distance in a source file between
two locations, in lines (zero if the locations are in different
files), and $\mathit{not\_same\_file}$ is 0/1.
